Approximation as Differentiation notes

### 2025-04-02 notes/sec/cmon-enriched.tex
Start on enriched Yoneda.

\begin{center}
\begin{tikzcd}[column sep=2.7cm]
   \Hom{C}{Y}{Z} \tensor \Hom{C}{X}{Y} \arrow[r, "\comp_{X,Y,Z}"] \arrow[d, "\Hom{C}{-}{W}_{Y,Z}\,\tensor\,\Hom{C}{-}{W}_{X,Y}"'] & \Hom{C}{X}{Z} \arrow[d, "\Hom{C}{-}{W}_{X,Z}"] \\
   \Hom{\mathscr{V}}{\Hom{C}{Z}{W}}{\Hom{C}{Y}{W}} \tensor \Hom{\mathscr{V}}{\Hom{C}{Y}{W}}{\Hom{C}{X}{W}} \arrow[r, "\comp_{\Hom{C}{X}{W},\Hom{C}{Y}{W},\Hom{C}{Z}{W}}"'] & \Hom{\mathscr{V}}{\Hom{C}{Z}{W}}{\Hom{C}{X}{W}}
\end{tikzcd}
\end{center}

\noindent \todo{Then there is an enriched version of the Yoneda embedding, namely a functor
$\Yoneda_{\mathscr{V}}: C \to \Func{C^\op}{\mathscr{V}}_{\mathscr{V}}$ analogous to the above which is itself
$\mathscr{V}$-enriched.}

>>>>

\begin{center}
\begin{tikzcd}[column sep=2.7cm]
   \Hom{C}{Z}{Y} \tensor \Hom{C}{Y}{X} \arrow[r, "\comp_{X,Y,Z}"] \arrow[d, "\Hom{C}{-}{W}_{Y,Z}\,\tensor\,\Hom{C}{-}{W}_{X,Y}"'] & \Hom{C}{Z}{X} \arrow[d, "\Hom{C}{-}{W}_{X,Z}"] \\
   \Hom{\mathscr{V}}{\Hom{C}{Y}{W}}{\Hom{C}{Z}{W}} \tensor \Hom{\mathscr{V}}{\Hom{C}{X}{W}}{\Hom{C}{Y}{W}} \arrow[r, "\comp_{\Hom{C}{X}{W},\Hom{C}{Y}{W},\Hom{C}{Z}{W}}"'] & \Hom{\mathscr{V}}{\Hom{C}{X}{W}}{\Hom{C}{Z}{W}}
\end{tikzcd}
\end{center}

\noindent \todo{Then there is an enriched version of the Yoneda embedding, namely a functor
$\Yoneda_{\mathscr{V}}: C \to \Func{C^\op}{\mathscr{V}}_{\mathscr{V}}$ analogous to $\Yoneda$ which is itself
$\mathscr{V}$-enriched.}
